Modern Graph Generators: A Survey

### 2018-11-09 generators_LinkedData.tex
last page 10 - iThenticate

\paragraph{IIMB} Contrary to the previous work, ~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching defined as follows: Given two instances $i_1$ and $i_2$, belonging to the same ontology or to different ontologies, instance matching is defined as a function $Im(i_1, i_2) \rightarrow \{0, 1\}$,  where $1$ denotes the fact that $i_1$ and $i_2$ are referred to the same real-world object and $0$ denotes the fact that $i_1$ and $i_2$ are referred to different objects. It targets the domain of movie data which contains 15 named classes, 5 object properties and 13 datatype properties. The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}. The data generator corresponds to a data modifier which simulates differences between the data. In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties representation, different aggregation criteria for properties representation, or missing values specification) and logical heterogeneity (such as instantiation on different subclasses of the same superclass or instantiation on disjoint classes).

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, models an e-commerce domain where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write~\cite{Bizer09theberlin}.
The benchmark comes equipped with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product. The data generator supports the creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc. BSBM can output two representations -- an RDF representation and a purely relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.

>>>>

\paragraph{IIMB} Contrary to the previous work, Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching. Given two instances $i_1$ and $i_2$ adhering to the same ontology or to different ontologies, instance matching is defined as a function $Im(i_1, i_2) \rightarrow \{0, 1\}$,  where $i_1$ and $i_2$ can be mapped to the same real-world object (in which case the function maps to $1$) or $i_1$ and $i_2$ are referred to different objects (in which case the function maps to $0$). It targets the domain of movie data which contains 15 named classes, along with 5 object properties and 13 datatype properties. The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}. The data generator corresponds to a data modifier which simulates differences between the data. In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as instantiation on different subclasses of the same superclass or instantiation on disjoint classes).

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce domain where types Product, Offer and Vendor model the relationships between products and the vendors offering them, while types Person and Review model the relationships between users and product reviews written by these users~\cite{Bizer09theberlin}.
The benchmark comes equipped with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product. The data generator is capable of producing arbitrarily large datasets using the number of products $n$ as scale factor.  The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc. BSBM can output two representations, i.e. an RDF representation along with a relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.
